Clustering of Last.fm Music Artists

### 2015-05-04 MSDgroupwriteup.tex
larger images

Using a coordinate ascent algorithm over 100 iterations, each row ($u_i$) and column ($v_j$) of the training matrix is then updated (see equations \ref{eq1} and \ref{eq2}) in order to maximize the log joint likelihood (see equation \ref{eq3}).

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png} 
   \caption{(how close our prediction is as compared to the actual normalized play count in the testing set }
   \label{fig:rmseplot}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2in]{C9LAAAAABJRU5ErkJggg==.png} 
   \caption{log joint likelihood of the training set as a function of iteration }
   \label{fig:likeplot}
\end{figure}

>>>>

Using a coordinate ascent algorithm over 100 iterations, each row ($u_i$) and column ($v_j$) of the training matrix is then updated (equations \ref{eq1} and \ref{eq2}) in order to maximize the log joint likelihood (equation \ref{eq3}).

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{h845BuzFO9CNgAAAABJRU5ErkJggg==.png} 
   \caption{how close our prediction is as compared to the actual normalized play count in the testing set }
   \label{fig:rmseplot}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{C9LAAAAABJRU5ErkJggg==.png} 
   \caption{log joint likelihood of the training set as a function of iteration }
   \label{fig:likeplot}
\end{figure}
